\begin{thebibliography}{10}

\bibitem{GNSS}
Bernhard Hofmann-Wellenhof, Herbert Lichtenegger and Elmar Wasle. \textit{GNSS – Global Navigation Satellite Systems: GPS, GLONASS, Galileo, and more}. Springer Science \& Business Media, 2007 [cited 2018-01-10], ISBN 9783211730171.

\bibitem{GNSSGPS}
AviationChief. \textit{Global Navigation Satellite System (GNSS) Global Positioning Satellite (GPS) System} [online]. AviationChief.Com, 2017 [cited 2018-01-15]. Available at: \url{http://www.aviationchief.com/gps-system.html}

\bibitem{LocalizationApproaches}
Xinglin Piao, Yong Zhang, Tingshu Li, Yongli Hu, Hao Liu, Ke Zhang and Yun Ge. \textit{RSS Fingerprint Based Indoor Localization Using Sparse Representation with Spatio-Temporal Constraint} [online]. National Center for Biotechnology Information, 2016 [cited 2018-01-14], Available at: \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5134504/}

\bibitem{PedestrianDeadReckoning}
Stéphane Beauregard and Harald Haas. \textit{Pedestrian Dead Reckoning: Basis for Personal Positioning} [online]. School of Engineering and Science
International University Bremen, 2006, Available at: \url{http://ave.dee.isep.ipp.pt/~lbf/PINSFUSION/BeHa06.pdf}

\bibitem{AaPLocalisation}
Gabriel Deak, Kevin Curran and Joan Condell. \textit{A survey of active and passive indoor localisation systems}. In: \textit{Computer Communications}. Elsevier, 2012 [cited 2018-01-11], Volume 35, Issue 16, ISSN: 0140-3664.

\bibitem{RAinWILTaS}
Zahid Farid, Rosdiadee Nordin, and Mahamod Ismail. \textit{Recent Advances in Wireless Indoor Localization Techniques and System} [online]. School of Electrical, Electronics \& System Engineering, University Kebangsaan Malaysia (UKM), 2013 [cited 2018-01-15], Available at: \url{http://downloads.hindawi.com/journals/jcnc/2013/185138.pdf}

\bibitem{LTinWSN}
Shweta Singh, Ravi Shakya and Yaduvir Singh. \textit{Localization techniques in wireless sensor networks} [online]. Department of Computer Science,
Ideal Institute of Technology, Ghaziabad, 2015 [cited 2018-01-15], ISSN: 0975-9646, Available at: \url{https://pdfs.semanticscholar.org/6299/85defbf9cc1a937a1b88c9c2a893552e3d89.pdf}

\bibitem{AoALforWSN}
Paweł Kułakowski, Javier Vales-Alonso, Esteban Egea-López, Wiesław Ludwin and Joan García-Haro. \textit{Angle-of-arrival localization based on antenna arrays for wireless sensor networks} [online]. In: \textit{Computers \& Electrical Engineering}. Elsevier, 2010 [cited 2018-01-15], Volume 36, Issue 6, Pages 1181-1186. Available at: \url{http://ai2-s2-pdfs.s3.amazonaws.com/17c6/0e17c4e72cc3fd821e12169c1c2ca7736bd4.pdf}

\bibitem{IILUBLEB}
Pavel Kriz, Filip Maly, and Tomas Kozel. \textit{Improving Indoor Localization Using Bluetooth Low Energy Beacons} [online]. In: \textit{Mobile Information Systems}. Hindawi Publishing Corporation, 2016 [cited 2018-01-15], Volume 2016, Article ID 2083094. Available at: \url{https://www.hindawi.com/journals/misy/2016/2083094/abs/}

\bibitem{TvTHGPSRW}
GISGeography. \textit{Trilateration vs Triangulation – How GPS Receivers Work} [online]. GISGeography.com, 2018 [cited 2018-01-15]. Available at: \url{http://gisgeography.com/trilateration-triangulation-gps/}

\bibitem{HPwAA}
Kenjirou Fujii, Yoshihiro Sakamoto, Wei Wang, Hiroaki Arie, Alexander Schmitz and Shigeki Sugano. \textit{Hyperbolic Positioning with Antenna Arrays and Multi-Channel Pseudolite for Indoor Localization} [online]. MDPI AG, Basel, 2015 [cited 2018-01-15]. Available at: \url{http://www.mdpi.com/1424-8220/15/10/25157/htm}

\bibitem{PLTaA}
David Munoz, Frantz Bouchereau Lara, Cesar Vargas and Rogerio Enriquez-Caldera. \textit{Position Location Techniques and Applications}. Elsevier Science Publishing Co Inc, 2009 [cited 2018-01-15], ISBN: 9780080921938. Available at: \url{http://www.mdpi.com/1424-8220/15/10/25157/htm}

\bibitem{AoA}
Group 891: Wireless Location. \textit{ANGULATION: AOA (Angle Of Arrival)} [online]. DEPARTMENT OF ELECTRONIC SYSTEMS, Aalborg University, 2010 [cited 2018-01-15]. Available at: \url{http://kom.aau.dk/group/10gr891/methods/Triangulation/Angulation/ANGULATION.pdf}

\bibitem{RofAoA}
Jais, M. I., Ehkan, P., Ahmad, R. B., Ismail, I., Sabapathy, T., and Jusoh, M. \textit{Review of angle of arrival (AOA) estimations through received signal strength indication (RSSI) for wireless sensors network (WSN)} [online]. In: Computer, Communications, and Control Technology (I4CT), 2015 International Conference on. IEEE, 2015, [cited 2018-01-16], p. 354-359. Available at: \url{https://www.researchgate.net/profile/Phaklen_Ehkan/publication/283476641_Review_of_angle_of_arrival_AOA_estimations_through_received_signal_strength_indication_RSSI_for_wireless_sensors_network_WSN/links/564106b008aebaaea1f6d6e5/Review-of-angle-of-arrival-AOA-estimations-through-received-signal-strength-indication-RSSI-for-wireless-sensors-network-WSN.pdf}

\bibitem{QAoA}
Quuppa Oy. \textit{Quuppa Intelligent Locating System} [online]. 2018 [cited 2018-01-16]. Available at: \url{http://quuppa.com/technology/}

\bibitem{ILWTP}
Krishna Chintalapudi, Anand Padmanabha Iyer, and Venkata N. Padmanabhan. \textit{Indoor Localization Without the Pain} [online]. In: Proceedings of the sixteenth annual international conference on Mobile computing and networking, 2010 [cited 2018-01-16], Available at: \url{http://dl.acm.org/citation.cfm?id=1860016}

\bibitem{RSSFofIFD}
Xiaoyang Wen, Wenyuan Tao, Chung-Ming Own, and Zhenjiang Pan. \textit{On the Dynamic RSS Feedbacks of Indoor Fingerprinting Databases for Localization Reliability Improvement} [online]. Sensors, 2016 [cited 2018-01-16], Available at: \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5017443/}

\bibitem{WiFiLBS}
Cisco. \textit{Wi-Fi Location-Based Services 4.1 Design Guide - Location Tracking Approaches} [online]. Cisco, 2018 [cited 2018-01-16], Available at: \url{https://www.cisco.com/c/en/us/td/docs/solutions/Enterprise/Mobility/WiFiLBS-DG/wifich2.html}

\bibitem{LSfUC}
Jeffrey Hightower and Gaetano Borriello. \textit{Location systems for ubiquitous computing} [online]. Computer, 2001 [cited 2018-01-17], 34.8: 57-66. Available at: \url{http://www.csd.uoc.gr/~hy439/lectures11/hightower2001survey.pdf}

\bibitem{LSAWIFI}
COOK, B., et al. \textit{Location by scene analysis of wi-fi characteristics} [online]. Relation, 2009 [cited 2018-01-17], 10.1.119: 6216. Available at: \url{http://www.ee.ucl.ac.uk/lcs/previous/LCS2006/2.pdf}

\bibitem{DRNS}
Levi, R.W. and Judd, T. \textit{Dead reckoning navigational system using accelerometer to measure foot impacts} [online]. Google Patents, 1996 [cited 2018-01-17]. Available at: \url{https://www.google.com/patents/US5583776}

\bibitem{IDRAIP}
Z. Zhou, T. Chen, L. Xu. \textit{An Improved Dead Reckoning Algorithm for Indoor Positioning Based on Inertial Sensors} [online]. In: Advances in Engineering Research, 2015 [cited 2018-01-17]. ISBN: 978-94-62520-71-4. Available at: \url{https://www.atlantis-press.com/proceedings/eame-15/22314}

\bibitem{IPBLEIUMWD}
NAKAJIMA, Naoki, et al. \textit{Improving Precision of BLE-based Indoor Positioning by Using Multiple Wearable Devices} [online]. In: Adjunct Proceedings of the 13th International Conference on Mobile and Ubiquitous Systems: Computing Networking and Services. ACM, 2016 [cited 2018-03-26]. p. 118-123. Available at: \url{https://dl.acm.org/citation.cfm?id=3004041}

\bibitem{SmartFix}
WANG, Xiaoliang; XU, Ke; LI, Ziwei. \textit{SmartFix: Indoor Locating Optimization Algorithm for Energy-Constrained Wearable Devices.} In: Wireless Communications and Mobile Computing, 2017 [cited 2018-03-26]. Available at: \url{https://dl.acm.org/citation.cfm?id=3004041}

\bibitem{TinyLoc}
W. Xiaoliang, X. Ke, Y. Zheng, and Z. Ge. \textit{Tinyloc: Indoor localization for energy-constrained wearable devices} [online]. In: Chinese Journal of Computers, 2016 (Chinese), [cited 2018-03-26]. Available at: \url{http://www.cnki.net/kcms/detail/11.1826.TP.20161106.1649.002.html}

\bibitem{MoLoc}
SUN, Wei, et al. \textit{MoLoc: On distinguishing fingerprint twins} [online]. In: Distributed Computing Systems (ICDCS), 2013 IEEE 33rd International Conference on. IEEE, 2013 [cited 2018-03-26]. p. 226-235. Available at: \url{http://ieeexplore.ieee.org/abstract/document/6681592/}

\bibitem{SWvsSP}
HOELZL, Gerold, et al. \textit{Size does matter-positioning on the wrist a comparative study: Smartwatch vs. smartphone} [online]. In: Pervasive Computing and Communications Workshops (PerCom Workshops), 2017 IEEE International Conference on. IEEE, 2017 [cited 2018-03-30]. p. 703-708.

\bibitem{WIGA}
Marziah Karch. \textit{What Is Google Android?} [online]. Lifewire, 2017 [cited 2018-01-17]. Available at: \url{https://www.lifewire.com/what-is-google-android-1616887}

\bibitem{AOSP}
Android. \textit{Android Open Source Code} [online]. Android.com, 2018 [cited 2018-01-17]. Available at: \url{https://source.android.com/}

\bibitem{AD}
Android. \textit{Android Developers} [online]. Android.com, 2018 [cited 2018-01-17]. Available at: \url{https://developer.android.com/index.html}

\bibitem{UtCoAWO}
Renju Liu and Felix Xiaozhu Lin. \textit{Understanding the Characteristics of Android Wear OS} [online]. In: Proceedings of the 14th Annual International Conference on Mobile Systems, Applications, and Services. ACM, 2016. p. 151-164. Available at: \url{https://athena.smu.edu.sg/mobisys/backend/mobisys/assets/paper_list/pdf_version/paper_12.pdf}

\bibitem{MIWD}
Samuel Gibbs. \textit{10 most influential wearable devices} [online]. Guardian News, 2017 [cited 2018-01-18]. Available at: \url{https://www.theguardian.com/technology/2017/mar/03/10-most-influential-wearable-devices}

\bibitem{GSWWDS}
Gartner, Inc. \textit{Gartner Says Worldwide Wearable Device Sales to Grow 17 Percent in 2017} [online]. Gartner, Inc., 2017 [cited 2018-01-18]. Available at: \url{https://www.gartner.com/newsroom/id/3790965}

\bibitem{SoASTaD}
Bahman Rashidi and Carol Fung. \textit{A Survey of Android Security Threats and Defenses} [online]. JoWUA, 2015, [cited 2018-01-19]. Available at: \url{https://www.researchgate.net/profile/Bahman_Rashidi2/publication/282365848_A_Survey_of_Android_Security_Threats_and_Defenses/links/560ec06908ae6b29b499a51f/A-Survey-of-Android-Security-Threats-and-Defenses.pdf}

\bibitem{ASIMPD}
Parvez Faruki, Ammar Bharmal, Vijay Laxmi, Vijay Ganmoor, Manoj Singh Gaur and Mauro Conti. \textit{Android Security: A Survey of Issues, Malware Penetration and Defenses} [online]. IEEE Communications Surveys and Tutorials, 17(2), pp. 998-1022, 2015, [cited 2018-01-19]. Available at: \url{http://dx.doi.org/10.1109/COMST.2014.2386139}

\bibitem{NoAAiGPS}
Statista. \textit{Number of available applications in the Google Play Store from December 2009 to December 2017} [online]. Statista, 2018, [cited 2018-01-19]. Available at: \url{https://www.statista.com/statistics/266210/number-of-available-applications-in-the-google-play-store/}

\bibitem{NoAA}
AppBrain. \textit{Number of Android applications} [online]. AppBrain, 2018, [cited 2018-01-19]. Available at: \url{https://www.appbrain.com/stats/number-of-android-apps}

\bibitem{CSUITW}
LIU, Xing, et al. \textit{Characterizing Smartwatch Usage In The Wild} [online]. In: Proceedings of the 15th Annual International Conference on Mobile Systems, Applications, and Services. ACM, 2017 [cited 2018-01-19]. p. 385-398. Available at: \url{https://pdfs.semanticscholar.org/0cc2/4bccc3067ed688e576603bc6bab0e5e1b1db.pdf}

\bibitem{UCAW}
Liu, Renju, and Felix Xiaozhu Lin. \textit{Understanding the Characteristics of Android Wear OS} [online]. In: Proceedings of the 14th Annual International Conference on Mobile Systems, Applications, and Services. ACM, 2016 [cited 2018-01-19], p. 151-164. Available at: \url{https://athena.smu.edu.sg/mobisys/backend/mobisys/assets/paper_list/pdf_version/paper_12.pdf}

\bibitem{AWPaS}
Sandra Henshaw. \textit{Android Wear Problems (and Solutions!)} [online]. Tiger Mobiles Limited, 2016 [cited 2018-01-20]. Available at: \url{https://www.tigermobiles.com/2016/01/android-wear-problems-and-solutions/}

\bibitem{WAWP}
Simon Hill. \textit{10 of the worst Android Wear problems, and how to fix them} [online]. Designtechnica Corporation, 2017 [cited 2018-01-20]. Available at: \url{https://www.digitaltrends.com/wearables/android-wear-problems/}

\bibitem{TOAW}
ADNAN F. \textit{Tizen overtakes Android Wear in smartwatch market share} [online]. SamMobile, 2017 [cited 2018-01-20]. Available at: \url{https://www.sammobile.com/2017/05/11/tizen-overtakes-android-wear-in-smartwatch-market-share/}

\bibitem{AW2UG}
Paul Lamkin. \textit{Android Wear 2.0: Ultimate guide to the major smartwatch update} [online]. Wareable, 2017 [cited 2018-01-20]. Available at: \url{https://www.wareable.com/android-wear/android-wear-update-everything-you-need-to-know-2735}

\bibitem{AW2WN}
Elyse Betters and Chris Hall. \textit{Android Wear 2.0: What's new in the major software update for watches?} [online]. Pocket-lint Limited, 2017 [cited 2018-01-20]. Available at: \url{https://www.pocket-lint.com/smartwatches/news/google/139007-android-wear-2-0-what-s-new-in-the-major-software-update-for-watches}

\bibitem{AW2N}
Chris Martin. \textit{Android Wear 2.0 news: release date and features} [online]. Tech Advisor, 2017 [cited 2018-01-20]. Available at: \url{https://www.techadvisor.co.uk/new-product/google-android/android-wear-2-3640616/}

\bibitem{DoAW}
Android Developers. \textit{Designing for Android Wear} [online]. Android, 2018 [cited 2018-01-20]. Available at: \url{https://developer.android.com/design/wear/index.html}

\bibitem{WIGA}
Elyse Betters. \textit{What is Google Assistant, how does it work, and which devices offer it?} [online]. Pocket-lint Limited, 2018 [cited 2018-01-20]. Available at: \url{https://www.pocket-lint.com/apps/news/google/137722-what-is-google-assistant-how-does-it-work-and-which-devices-offer-it}

\bibitem{ASGA}
DAN MOREN. \textit{Alexa vs. Siri vs. Google Assistant: Which Smart Assistant Wins?} [online]. Tom's Guide, 2017 [cited 2018-01-20]. Available at: \url{https://www.tomsguide.com/us/alexa-vs-siri-vs-google,review-4772.html}

\bibitem{VACCGASAB}
Digital Trends Staff. \textit{Virtual assistant comparison: Cortana, Google Assistant, Siri, Alexa, Bixby} [online]. Digital Trends, 2017 [cited 2018-01-20]. Available at: \url{https://www.digitaltrends.com/computing/cortana-vs-siri-vs-google-now/}

\bibitem{CAGACS}
Brian Heater. \textit{Comparing Alexa, Google Assistant, Cortana and Siri smart speakers} [online]. TechCrunch, 2017 [cited 2018-01-20]. Available at: \url{https://techcrunch.com/2017/10/08/comparing-alexa-google-assistant-cortana-and-siri-smart-speakers/}

\bibitem{GASBAC}
Joe Hindy. \textit{Google Assistant vs Siri vs Bixby vs Amazon Alexa vs Cortana – Best virtual assistant showdown!} [online]. Android Authority, 2017 [cited 2018-01-20]. Available at: \url{https://www.androidauthority.com/google-assistant-vs-siri-vs-bixby-vs-amazon-alexa-vs-cortana-best-virtual-assistant-showdown-796205/}

\bibitem{TOSBHR}
Haroon Q. Raja. \textit{Tizen OS: Brief History, Roots, and Current Status} [online]. xda-developers, 2013 [cited 2018-04-16]. Available at: \url{https://www.xda-developers.com/tizen-os-brief-history-roots-and-current-status/}

\bibitem{TizenM}
\textit{Tizen Members} [online]. Tizen Association, 2014 [cited 2018-04-16]. Available at: \url{https://www.tizenassociation.org/members/}

\bibitem{TizenAbout}
\textit{Tizen} [online]. Tizen Project, 2012 [cited 2018-04-16]. Available at: \url{https://www.tizen.org/about}

\bibitem{TizenDev}
\textit{Tizen Developers} [online]. Tizen Project, 2012 [cited 2018-04-16]. Available at: \url{https://developer.tizen.org/development/tizen-studio}

\bibitem{ATOHAWWC}
Rhiannon Williams. \textit{A timeline of how the Apple Watch was created} [online]. The Telegraph, 2015 [cited 2018-04-17]. Available at: \url{http://www.businessinsider.com/a-timeline-of-how-the-apple-watch-was-created-2015-3}

\bibitem{WOS9To5MAC}
\textit{watchOS} [online]. 9to5Mac, 2018 [cited 2018-04-17]. Available at: \url{https://9to5mac.com/guides/watchos/}

\bibitem{AppleDev}
\textit{Apple Developer} [online]. Apple, 2018 [cited 2018-04-17]. Available at: \url{https://developer.apple.com/}

\bibitem{HTFAIAAW}
Jason Fitzpatrick. \textit{How to Find and Install Apps on Your Apple Watch} [online]. How-To Geek, 2015 [cited 2018-04-17]. Available at: \url{https://www.howtogeek.com/230224/how-to-find-and-install-apps-on-your-apple-watch/}

\bibitem{NFFAWSW}
Mishaal Rahman. \textit{No future for Android Wear in Samsung’s Watches} [online]. xda-developers, 2016 [cited 2018-04-16]. Available at: \url{https://www.xda-developers.com/report-samsung-is-done-with-android-wear-os/}

\bibitem{XRN4FPS}
GSMArena. \textit{Xiaomi Redmi Note 4 - Full phone specifications} [online]. GSMArena, 2018 [cited 2018-01-21]. Available at: \url{https://www.gsmarena.com/xiaomi_redmi_note_4-8531.php}

\bibitem{XRN4LTE}
XiaomiMobile. \textit{Xiaomi Redmi Note 4 LTE} [online]. XiaomiMobile, 2018 [cited 2018-01-21]. Available at: \url{https://xiaomimobile.cz/xiaomi-redmi-note-4-pro-lte-global.html?search_query=note+4&results=16}

\bibitem{BAWW}
Android Authority Team. \textit{Best Android Wear watches (old version)} [online]. Android Authority, 2017 [cited 2018-01-21]. Available at: \url{https://www.androidauthority.com/best-android-watches-572773/}

\bibitem{BAWW18}
James Peckham. \textit{Best Android Wear watch 2018: our list of the top Google OS smartwatches} [online]. TechRadar, 2017 [cited 2018-01-21]. Available at: \url{http://www.techradar.com/news/wearables/every-android-wear-smartwatch-in-the-world-today-1288283}

\bibitem{BAWW17}
Michael Simon. \textit{Best Android Wear watches of 2017} [online]. PCWorld, 2017 [cited 2018-01-21]. Available at: \url{https://www.pcworld.com/article/3209668/android/best-android-wear-watches-of-2017.html}

\bibitem{LGWSP}
LG Electronics. \textit{LG Watch Sport™ - AT\&T} [online]. LG Electronics, 2018 [cited 2018-01-22]. Available at: \url{http://www.lg.com/us/smart-watches/lg-W280A-sport}

\bibitem{LGWST}
LG Electronics. \textit{LG Watch Style} [online]. LG Electronics, 2018 [cited 2018-01-22]. Available at: \url{http://www.lg.com/us/smart-watches/lg-W270-Titanium-style}

\bibitem{HW2}
HUAWEI Technologies Co. \textit{HUAWEI WATCH 2} [online]. HUAWEI Technologies Co., 2018 [cited 2018-01-22]. Available at: \url{http://consumer.huawei.com/en/wearables/watch2/specs/}

\bibitem{PM600}
Polar Electro. \textit{Polar M600} [online]. Polar Electro, 2018 [cited 2018-01-22]. Available at: \url{https://support.polar.com/e_manuals/M600/Polar_M600_user_manual_English/Content/technical-specifications.htm}

\bibitem{AZW3}
ASUSTeK Computer Inc. \textit{ASUS ZenWatch 3} [online]. ASUSTeK Computer Inc., 2018 [cited 2018-01-22]. Available at: \url{https://www.asus.com/us/ZenWatch/ASUS-ZenWatch-3-WI503Q/specifications/}

\bibitem{HtPAWW}
Adam Conway. \textit{How to Pair Android Wear Watches to New Phones without Factory Resetting} [online]. xda-developers, 2017 [cited 2018-01-22]. Available at: \url{https://www.xda-developers.com/pair-android-wear-without-factory-reset/}

\bibitem{AWITFNM}
Dennis Troper. \textit{Android Wear, it’s time for a new name} [online]. Google, 2018 [cited 2018-04-02]. Available at: \url{https://www.blog.google/products/wear-os/android-wear-its-time-new-name/}

\bibitem{IPSBOBLE}
Locatify. \textit{Indoor Positioning Systems based on BLE Beacons – Basics} [online]. Locatify, 2015 [cited 2018-01-27]. Available at: \url{https://locatify.com/blog/indoor-positioning-systems-ble-beacons/}

\bibitem{10TABB}
Patrick Leddy. \textit{10 Things About Bluetooth Beacons You Need to Know} [online]. pulsate, 2015 [cited 2018-01-27]. Available at: \url{http://academy.pulsatehq.com/bluetooth-beacons}

\bibitem{RMPFEB}
The Estimote Team Blog. \textit{Reality matters — Preorder for Estimote Beacons available, shipping this summer} [online]. Estimote, Inc., 2013 [cited 2018-01-27]. Available at: \url{http://blog.estimote.com/post/57087851702/preorder-for-estimote-beacons-available-shipping}

\bibitem{ESDKfA}
\textit{Estimote SDK for Android} [online]. Estimote, 2018 [cited 2018-01-22]. Available at: \url{https://github.com/Estimote/Android-SDK}

\bibitem{PMRIL}
Radek Brůha. \textit{Pokročilé metody rádiové indoor lokalizace} [online]. Univerzita Hradec Králové, 2017 [cited 2018-01-22]. Available at: \url{https://theses.cz/id/jss047}

\bibitem{ABL}
\textit{Android Beacon Library} [online]. Radius Networks, 2018 [cited 2018-01-22]. Available at: \url{https://altbeacon.github.io/android-beacon-library/}

\bibitem{AltB}
\textit{AltBeacon} [online]. AltBeacon, 2018 [cited 2018-01-22]. Available at: \url{http://altbeacon.org/}

\bibitem{EDDF}
\textit{Eddystone format} [online]. Google Developers, 2018 [cited 2018-01-22]. Available at: \url{https://developers.google.com/beacons/eddystone}

\bibitem{NOSQLDB}
\textit{NOSQL Databases} [online]. NoSQL, 2018 [cited 2018-01-27]. Available at: \url{http://nosql-database.org/}

\bibitem{NOSQLDB}
\textit{NOSQL Databases} [online]. NoSQL, 2018 [cited 2018-01-27]. Available at: \url{http://nosql-database.org/}

\bibitem{GSWCBS}
Brown, Martin C. \textit{Getting Started with Couchbase Server: Extreme Scalability at Your Fingertips} [online]. O'Reilly Media, Inc., 2012 [cited 2018-01-27]. Available at: \url{https://books.google.cz/books?hl=cs&lr=&id=5xu33G9LGkMC&oi=fnd&pg=PR5&dq=Couchbase&ots=nrw7O3HiVh&sig=6qmpVJLxwdOK9RRZsICHUfsD2wI&redir_esc=y#v=onepage&q&f=false}

\bibitem{WINQL}
\textit{What is N1QL?} [online]. Couchbase, 2018 [cited 2018-01-27]. Available at: \url{https://www.couchbase.com/products/n1ql}

\bibitem{ERDMS}
\textit{Explain Relational Database Management System (RDBMS)} [online]. W3Schools, 2016 [cited 2018-01-23]. Available at: \url{http://whatisdbms.com/explain-relational-database-management-system-rdbms/}

\bibitem{WISQLITE}
\textit{What Is SQLite} [online]. SQLite Tutorial, 2018 [cited 2018-01-23]. Available at: \url{http://www.sqlitetutorial.net/what-is-sqlite/}

\bibitem{WTM}
Sterling Quinn, John A. Dutto. \textit{Why tiled maps?} [online]. e-Education Institute, College of Earth and Mineral Sciences, The Pennsylvania State University, 2018 [cited 2018-04-08]. Available at: \url{https://www.e-education.psu.edu/geog585/node/706}

\bibitem{TileView}
Mike Dunn. \textit{TileView} [online]. Mike Dunn, 2016 [cited 2018-04-11]. Available at: \url{https://github.com/moagrius/TileView}

\bibitem{TileViewWiki}
Mike Dunn. \textit{Creating Tiles} [online]. Mike Dunn, 2016 [cited 2018-04-11]. Available at: \url{https://github.com/moagrius/TileView/wiki/Creating-Tiles}

\bibitem{SOTAJS}
\textit{Scheduling of tasks with the Android JobScheduler - Tutorial} [online]. vogella, 2017 [cited 2018-04-06]. Available at: \url{http://www.vogella.com/tutorials/AndroidTaskScheduling/article.html}

\bibitem{GTMDL}
\textit{Google Tag Manager DataLayer Explained} [online]. Analytics Mania, 2017 [cited 2018-04-08]. Available at: \url{https://www.analyticsmania.com/post/what-is-data-layer-in-google-tag-manager/}

\bibitem{HGAfC}
KELLY JR, James D.; DAVIS, Lawrence. \textit{A Hybrid Genetic Algorithm for Classification}. In: IJCAI. 1991 [cited 2018-04-13]. p. 645-650. Available at: \url{https://www.ijcai.org/Proceedings/91-2/Papers/006.pdf}

\end{thebibliography}